A Topic Model of Climate Change Literature

### 2017-05-03 main.tex
Update on Overleaf.

While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g. \citep[e.g.][]{minx2016negative,Sleeman2016}, this is the first application of topic models to gain an overview of the entire field.

@@

\begin{figure}
	%\includegraphics{}
    \caption{5 topics with most growth and 5 topics with biggest decline}
\end{figure}

>>>>

While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g. \citep[e.g.][]{minx2016negative,Grubert2016}, this is the first application of topic models to gain an overview of the entire field.

@@

\begin{figure}
	\includegraphics[width=\linewidth]{plots/hot_topics}
    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled}
\end{figure}
